Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-24 article.rnw
Correct spelling.

	\caption{%
		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
		The green line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_separated_statistics$aic}}) of the ungrouped model, in which all competition coefficients are fitted independently.
		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics$aic}}) of the full grouped model, where every pair os species shares a single interaction coefficient.
	}
	\label{fig:aic}
\end{figure}

>>>>

	\caption{%
		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
		The green line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_separated_statistics$aic}}) of the ungrouped model, in which all competition coefficients are fitted independently.
		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics$aic}}) of the full grouped model, where every pair of species shares a single interaction coefficient.
	}
	\label{fig:aic}
\end{figure}
